The Private School Network

### 2024-02-19 index.qmd
#12 add intro map
#14 add horizontal line for text slides

### Off-campus recruiting visits to high schools in Nashville

CRYSTAL: INSERT MAP HERE

@@

### Literature Review
#### Linkages between private schools and private universities
<hr>
Studies find attending private school increases college access, selectivity

@@

### Literature Review
#### Synthesis
<hr>
These two literatures have developed in isolation

@@

### Characteristics of universities in analysis sample

@@

kbl(univ_sample, align = c('l', 'l', rep('r', 13)), escape = F) %>% 
  collapse_rows(columns = 1, valign = 'middle') %>% 
  column_spec(4, width_min = '1.2in') %>% 
  column_spec(6, width_min = '1in') %>% 
  column_spec(8, width_min = '1in')
```
:::

### Characteristics of universities in analysis sample compared to data collection sample

@@

### Number of HS visits by public research universities

@@

### Number of HS visits by selective private universities

@@

### Proportional HS visits by public research universities

@@

### Proportional HS visits by selective private universities

@@

### One-mode percent matrix, all universities

@@

### One-mode network for all universities

@@

### Order 2 ego network of University of Notre Dame

@@

### Geographic region of visited private high schools

@@

### Religious affiliation of visited private high schools

@@

### Racial composition of visited HS, public universities

@@

### Racial composition of visited HS, private universities

@@

### High school ranking of visited private high schools

@@

<hr>

@@

### All recruiting visits, public research universities

@@

### One-mode public university percent matrix

@@

### One-mode network, public universities

@@

### One-mode private university percent matrix

@@

### For private universities, the percent of high schools visited by public universities

@@

### For public universities, the percent of high schools visited by private universities

@@

### Racial composition in the South, public universities

@@

### Racial composition in the South, private universities

>>>>

### Off-campus recruiting visits to high schools in Nashville {.caption}

<iframe src="./assets/maps/intro_map.html" width=100% height=100% allowtransparency="true"></iframe>

@@

### Literature Review
#### Linkages between private schools and private universities

Studies find attending private school increases college access, selectivity

@@

### Literature Review
#### Synthesis

These two literatures have developed in isolation

@@

### Characteristics of universities in analysis sample {.caption}

@@

kbl(univ_sample, align = c('l', 'l', rep('r', 13)), escape = F) %>% 
  collapse_rows(columns = 1, valign = 'middle') %>% 
  column_spec(4, width_min = '1.4in') %>% 
  column_spec(6, width_min = '1in') %>% 
  column_spec(8, width_min = '1in')
```
:::

### Characteristics of universities in analysis sample compared to data collection sample {.caption}

@@

### Number of HS visits by public research universities {.caption}

@@

### Number of HS visits by selective private universities {.caption}

@@

### Proportional HS visits by public research universities {.caption}

@@

### Proportional HS visits by selective private universities {.caption}

@@

### One-mode percent matrix, all universities {.caption}

@@

### One-mode network for all universities {.caption}

@@

### Order 2 ego network of University of Notre Dame {.caption}

@@

### Geographic region of visited private high schools {.caption}

@@

### Religious affiliation of visited private high schools {.caption}

@@

### Racial composition of visited HS, public universities {.caption}

@@

### Racial composition of visited HS, private universities {.caption}

@@

### High school ranking of visited private high schools {.caption}

@@

@@

### All recruiting visits, public research universities {.caption}

@@

### One-mode public university percent matrix {.caption}

@@

### One-mode network, public universities {.caption}

@@

### One-mode private university percent matrix {.caption}

@@

### For private universities, the percent of high schools visited by public universities {.caption}

@@

### For public universities, the percent of high schools visited by private universities {.caption}

@@

### Racial composition in the South, public universities {.caption}

@@

### Racial composition in the South, private universities {.caption}
